
%----------------------------------------------------------------------------------------
% PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
%\usepackage[<option1, option2>]{hyperref}
\documentclass{./sjkelly_resume} 					% Use the custom resume.cls style
\usepackage[compact]{titlesec} 					%compact section spacing
%\usepackage{mdwlist} %compact enumerating
%\usepackage{tabularx}
\setstretch{0.7}

%----------------------------------------------------------------------------------------
% NAME
%----------------------------------------------------------------------------------------
\name{Stephen Kelly} % Your name
\address{\large{14 Preston Ln.  $\bullet$  Hicksville, NY 11801}} % Your address
\address{\large{Github: sjkelly}} % Online Presence
\address{\large{kd2cca@gmail.com \\ 1-516-589-2698}} % Your phone number and email

\begin{document}
\titlespacing{\section}{0pt}{*0}{*0}
\titlespacing{\subsection}{0pt}{*0}{*0}

%----------------------------------------------------------------------------------------
% OBJECTIVE
%----------------------------------------------------------------------------------------
\begin{mainSection}{Objective}
	Interesting projects in mathematical modelling and computational geometry.
\end{mainSection}

%----------------------------------------------------------------------------------------
% EDUCATION SECTION
%----------------------------------------------------------------------------------------
\begin{mainSection}{Education}
	{Worcester Polytechnic Institute (WPI)}, {Worcester, Massachusetts} \hfill {Est. May. 2016 } \\ 
	\textbf{Bachelor of Science in Mathematical Sciences}\\
	{\small {\bf Related Coursework:} Numerical Methods, Vector and Tensor Calculus, Graph Theory, Mathematical Modeling with Differential Equations, Unified Robotics: Actuation, Unified Robotics: Sensing, Systems Programming, Statics}
\end{mainSection}


%----------------------------------------------------------------------------------------
% PROJECTS
%----------------------------------------------------------------------------------------
\begin{mainSection}{Related Projects}
	\begin{experienceSubsection}{Contributor}{March 2014 - Present}{Julia}{github.com/julialang}
		\item Contribute bugfixes and documentation to the core language and base library
		\item Maintain Meshes.jl package for 3D mesh loading, processing, and writing
		\item Submit fixes to packages for future compatiblity based on Julia development
	\end{experienceSubsection}
	\begin{experienceSubsection}{Open Source Independent Project}{July 2013 - Aug. 2013}{TextCAD}{github.com/textcad}
		\item Developed methods for 3D model description using object serialization in Python
		\item Wrote a parser with extensive unit tests to convert JSON files of serialized objects to OpenSCAD
		\item Explored methods of programmed parametric mechanical design using objects and datasets
		\item Implemented the final concepts in a parametric 2D gantry system using an ``H-Bot'' configuration
	\end{experienceSubsection}
	\begin{experienceSubsection}{Open Source Internship Project}{June 2013 - July 2013}{Test Fixture}{Ultimachine}
		\item Developed the mechanics, software, and schematics for a test fixture to benchmark completed circuit boards
		\item Used sensors and software to determine the condition of each circuit board and log results to a database
	\end{experienceSubsection}
\end{mainSection}

%----------------------------------------------------------------------------------------
% WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{mainSection}{Work Experience}
	\begin{experienceSubsection}{Voxel8}{Aug. 2014 - May 2015}{Software Engineer}{Somerville, Massachusetts}
		\item Led the development of a path planner for 3D printing of thermoplastic and conductive paste
		\item Researched, implemented, and documented geometric algorithms for use in path planning
		\item Worked with electric teams to update and patch printer firmware
	\end{experienceSubsection}
	\begin{experienceSubsection}{Lewis Group}{May 2014 - Aug. 2014}{Research Assistant}{Harvard University, Massachusetts}
		\item Researched existing path planners and architectual piplines for 3D printing
		\item Developed mesh slicing and polygon operation libraries
		\item Worked with researchers to develop path sequences for truss fabrication on 3D printers
	\end{experienceSubsection}
	\begin{experienceSubsection}{Advanced Manufacturing Research Institute}{Aug. 2013}{Fellow}{Rice University, Texas}
		\item Developed an open source toolchain for the inkjet printing of genetically modified bacteria
		\item Created appropriate firmware modifications to drive inkjet heads on a 3D printer
		\item Wrote path planning software for multiple inkjets in Python using OpenCV 
	\end{experienceSubsection}
	\begin{experienceSubsection}{Ultimachine}{Jan. 2013 - Aug. 2013}{Intern}{South Pittsburg, Tennessee}
		\item Developed open source hardware testing solutions for internal manufacturing processes
		\item Created product documentation and corresponding procedures
	\end{experienceSubsection}
	\begin{experienceSubsection}{Mill-Max Mfg.}{June 2012 - Aug. 2012}{Intern}{Oyster Bay, New York}
		\item Handled and organized customer data and engineering drawings
		\item Developed and implemented multi-material rapid prototyping systems for internal use
	\end{experienceSubsection}
	\begin{experienceSubsection}{WPI Washburn Machine Shops}{Sept. 2011 - Oct. 2012}{Lab Assistant}{WPI}
		\item Helped maintain the facilities by monitoring the labs and cleaning equipment
		\item Coordinated with Teaching Assistants to setup materials and machines for laboratory classes
	\end{experienceSubsection}
	\begin{experienceSubsection}{Panera Bread}{June 2010 - Nov. 2010}{Associate}{Hicksville, New York}
		\item Worked in a team to process guests' orders
		\item Maintained a fast paced work progression while completing secondary tasks
	\end{experienceSubsection}	
\end{mainSection}

%----------------------------------------------------------------------------------------
% SKILLS SECTION
%----------------------------------------------------------------------------------------
\begin{mainCompactSection}{Skills}

	\renewcommand{\tabcolsep}{0pt}

	\begin{tabular}{l l}

	
	\skillSubsection{Computer Systems}{GNU/Linux (Fedora, Debian/Ubuntu, Android), Windows, MacOS X}
	\skillSubsection{Office Software}{Microsoft Office(Word, Excel, PowerPoint), Libre Office, Google Drive}
	\skillSubsection{Development Environments}{Git, Subversion, Eclipse, QT Creator, Arduino}
	\skillSubsection{Mechanical Design Tools}{OpenSCAD, Auto/LibreCAD, SolidWorks, Fusion360}
	\skillSubsection{Computer Languages}{Julia, Python, C, C++, Javascript, \LaTeX}
	\skillSubsection{Certifications}{Technician FCC License (KD2CCA)}
	\skillSubsection{Languages}{English (Native), Spanish (Conversant)}
	\end{tabular}

\end{mainCompactSection}


%----------------------------------------------------------------------------------------
% ACTIVITIES
%----------------------------------------------------------------------------------------
%\begin{mainCompactSection}{Activities}
%	
%	\begin{generalSubsection}
%		{Lab Manager}{WPI}{2011 - Present}{CollabLab}
%	\end{generalSubsection}
%	\begin{generalSubsection}
%		{Member}{WPI}{2011 - Present}{SmartMouse}
%	\end{generalSubsection}	
%	\begin{generalSubsection}
%		{Founder}{WPI}{2012 - Present}{RepRap User Group}
%	\end{generalSubsection}	
%	\begin{generalSubsection}
%		{Treasurer}{WPI}{2013 - Present}{Running Club}
%	\end{generalSubsection}
%	\begin{generalSubsection}
%		{Member}{WPI}{2013 - Present}{Society for Industrial and Applied Mathematics}
%	\end{generalSubsection}
%\end{mainCompactSection}

%----------------------------------------------------------------------------------------
% AWARDS SECTION
%----------------------------------------------------------------------------------------
%\begin{mainCompactSection}{Awards}
	
%	\begin{generalSubsection}
%		{award name}{location}{dates}{type}
%	\end{generalSubsection}
	

%\end{mainCompactSection}

%----------------------------------------------------------------------------------------

\end{document}

